Plotting the Single-Electron Solution to Schr\"{o}dinger's Equation with OpenCL

### 2010-05-05 paper/paper.tex
More formulas and citations
Plots!

@@

MAKE SURE TO CITE MATHWORLD

>>>>

\begin{figure}
    \includegraphics[width=84.5mm]{strongPlotOne.pdf}
    \caption{Core Count vs. Runtime on the 4890 with a fixed resolution ($400\times400$)}
\end{figure}

\begin{figure}
    \includegraphics[width=84.5mm]{strongPlotTwo.pdf}
    \caption{Core Count vs. Speedup (measured against a single-core run) on the 4890 with a fixed resolution ($400\times400$); the orange line is the theoretical maximum speedup, given linear scaling and 50 execution units (800 cores / 16 cores per unit); the red line is a linear (1:1) speedup curve}
\end{figure}

@@
